Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Minor grammatical changes to section 3, 4.1 and 4.2

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut. The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$. The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
}
\label{fig:sizedefinition}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo. Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01. The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here. See \S\ref{sec:future} for further discussion.}
\beq
\label{eq:fiducial_model}
\rhalf = 0.01\rvir
\eeq
For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
\eeq
where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}. This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.

@@

As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation. We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut. The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$. The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the sample.
}
\label{fig:sizedefinition}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

As noted in \S\ref{sec:intro}, it was shown in \citet{kravtsov13} that galaxy sizes are on average proportional to the virial radius of their host halo. Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01. The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here. See \S\ref{sec:future} for further discussion.}
\beq
\label{eq:fiducial_model}
\rhalf = 0.01\rvir
\eeq
For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
\eeq
where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}. This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.

@@

As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level. This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation. We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.
